\section{Necron Factions}

\begin{multicols}{2}
\subsection{Charnovokh}

%TODO
\textbf{Advanced Reaction:}

\textbf{Dynasty Effect:}


\subsection{Maynarkh}

Maynarkh Dynasty Necron units gain the Necron Dynasty (Maynarkh) special rule, which grants the TODO: This advanced reaction and Cursed Awakening special rule. 

Any unit with the Necron Dynasty (Maynark) special rule and Character sub-type may take any of the following:
\begin{itemize}
	\item \quickref{Mark of the Flayer} special rule \dotfill 0 points.
	\item \quickref{Bloodswarm Scarabs} \dotfill 5 points.
\end{itemize}

Any unit with the Necron Dynasty (Maynark) special rule may take any of the following:
\begin{itemize}
	\item \quickref{Flensing Scarabs} \dotfill +10 points.
\end{itemize}

A Charnel Lychguard Phalanx with the Necron Dynasty (Maynarkh) special rule may take the following option:

One Charnel Lychguard may take:
\begin{itemize}
	\item \quickref{Dynastic Ankh} \dotfill +10 points
\end{itemize} 

%TODO
\textbf{Advanced Reaction:}

\textbf{Necron Dynasty (Maynarkh) (Cursed Awakening):} When a unit made up of entirely models with the Necron Dynasty (Maynarkh) special rule attacks during the Fight phase against an enemy unit that is Pinned, Falling Back, or outnubmered by the attack unit it gets a +1 to all To Wound or Armour Penetration rolls made during the Assault. Futhermore if one or more models with this special rule are part of a combat that results in a draw, then the side that includes one or more models at the end of the fight sub-phase with this special rule is counted as having won the combat by 1 point. If both sides include models with this special rule then the combat remains a draw. Models with the Decurion/Tesserarion Nemesor special ability may also take Charnel Lychguard as a part of the same Force Organization slot.

\textbf{Maynarkh:}


\subsection{Mephrit}

Mephrit Dynasty Necron units gain the Necron Dynasty (Mephrit) special rule, which grants the Solar Fury advanced reaction and Stellar Destruction special rule.

Any unit with the Necron Dynasty (Mephrit) special rule may take any of the following:
\begin{itemize}
	\item \quickref{Stellar Energetic Reactors} \dotfill +10 points.
\end{itemize}

\textbf{Advanced Reaction (Solar Fury):} This Advanced Reaction may be made once per battle during the opposing player’s Shooting phase when any enemy unit declares a Shooting Attack targeting a friendly unit under the Reactive player’s control composed entirely of models with the Necron Dynasty (Mephrit) special rule. Once the Active player has resolved all To Hit and To Wound rolls, and Armour Saves are made, but before any Damage Mitigation rolls are made or casualties removed, the Reactive player may make a Shooting Attack, targeting the unit that triggered this Reaction, with all weapons increasing their AP by 1 but gaining the Gets Hot special rule. To Hit rolls for weapons that already possess the Gets Hot special rule trigger that special rule on a roll of 1 or 2 during this Shooting Attack, instead of only on a 1. A unit that makes a Solar Fury as part of a Solar Fury Reaction may not make any attacks indirectly (without line of sight) including weapons with the Barrage special rule or other weapon or special rule that otherwise ignore line of sight, and Vehicles may only fire Defensive weapons. Template weapons used as part of a Solar Fury Reaction use the Wall of Death rule instead of firing normally.

\textbf{Necron Dynasty (Mephrit) (Stellar Destructors):}  When a unit made up of entirely models with the Necron Dynasty (Mephrit) special rule rolls for scatter with a Blast Weapon they roll a D6 instead of 2D6.

\textbf{Warlord Trait (Merciless Tyrant):}

\textit{Embodied by a merciless overlord whose heart is as relentless as the sun's fury, this warlord personifies the Mephrit Dynasty’s doctrine of overwhelming firepower and absolute ruthlessness. The Merciless Tyrant harnesses the destructive potential of Necron weaponry to its fullest extent, pushing the limits of their arsenal to unleash a storm of energy blasts upon their foes. Under his command, even the disciplined Necron legions become instruments of searing annihilation, their attacks intensified to a perilous edge, ready to burn through any opposition with a scorching, unyielding wrath.}

A Warlord with this Trait, and every model with the Infantry Unit Type in a unit it has joined with the Necron Dynasty (Mephriy) special rule may choose to roll an additional dice when making a Shooting Attack with any Rapid Fire, Assault or Heavy weapon that does not have the Blast or Template special rules, but these weapons gain the Gets Hot special rule for that Shooting Attack. If a Warlord and/or unit under the effect of this Trait makes the Solar Fury Reaction, then a single additional dice is added to the number of attacks made by each model after the effects of Solar Fury have been applied. In addition, whenever a Warlord with this Trait, and any unit it has joined, is the target of an enemy Shooting Attack it must make either the Return Fire or Solar Fury Reactions if possible – this Reaction does not cost a point of the Reactive player’s Reaction Allotment, but does not allow that unit to make any further Reactions in that Phase and does not allow the Solar Fury Reaction to be made more than once per battle. However, a Warlord with this Trait and any unit it has joined may make no other Reaction in any Phase, excepting only the Interceptor Advanced Reaction.


\subsection{Nephrekh}

Nephrekh Dynasty Necron units gain the Necron Dynasty (Nephrekh) special rule, which grants the Beings of Light advanced reaction and Translocation Beamers special rule.
%TODO: Equipment

\textbf{Advanced Reaction (Beings of Light):} This Advanced Reaction may be made once per battle during the opposing player’s Shooting phase when any enemy unit declares a Shooting Attack targeting a friendly unit with the Infantry Unit Type under the Reactive player’s control with the Necron Dynasty (Nephrekh) special rule. All models in the Reacting unit gain the Feel No Pain (5+) special rule against all Wounds inflicted as part of the Shooting Attack that triggered this Reaction. If the Reacting unit already has a version of the Feel No Pain (X) special rule, then this does not stack or increase that rule, and the Reacting player may choose to use any one of the Feel No Pain (X) special rules available to them. Once the Shooting Attack has been completely resolved, the Reactive player may make a Shooting Attack, targeting the unit that triggered this Reaction.

\textbf{Necron Dynasty (Nephrekh) (Translocation Beamers):} A unit made up of entirely models with the Necron Dynasty (Nephrekh) special rule has a 6+ Invulnerability Save and the Moves Through Cover special rule. 

\textbf{Nephrekh:}


\subsection{Nihilakh}

%TODO
\textbf{Advanced Reaction:}

\textbf{Dynasty Effect:}

\textbf{Nihilakh:}


\subsection{Novokh}

Novokh Dynasty Necron units gain the Necron Dynasty (Novokh) special rule, which grants the Blood Engrams advanced reaction and Awakened By Murder special rule.

Any unit with the Necron Dynasty (Novokh) special rule may take any of the following:
\begin{itemize}
	\item %Todo \dotfill +10 points.
\end{itemize}

\textbf{Advanced Reaction (Blood Engrams):} This Advanced Reaction may be made once per battle in the opposing player’s turn, when any enemy unit with one or more models within 12" of a friendly unit made up entirely of models with the Necron Dynasty (Novokh) special rule is moved during the Movement phase. Once the enemy unit that triggered this Reaction has been moved, but before any other units are moved, a single friendly unit made up entirely of models with the Necron Dynasty (Novokh) special rule that can draw a line of sight to the enemy unit that moved may immediately move up to a number of inches equal to twice the highest Initiative Characteristic in the unit and then declare a Charge targeting the enemy unit that moved if it is within 12". A Charge declared as part of this Reaction is resolved immediately (the enemy unit may not declare any Reaction against this Charge), and if successful the combat will be fought as normal in the following Assault phase, with a Charging unit with the Necron Dynasty (Novokh) special rule gaining all the normal benefits of Charging.

\textbf{Necron Dynasty (Novokh) (Awakened By Murder):} In the Fight sub-phase, after casualties have been removed but before determining which side has won, if this unit has caused unsaved wounds to the enemy unit it enters \textit{Engrammatic Blood Rage} until the end of the game. When in \textit{Engrammatic Blood Rage}, this unit gains the Fearless, Furious Charge (1), and Rage (1) special rules.

\textbf{Warlord Trait (Blood-Fueled Fury):}

\textit{Emanating an aura of unquenchable rage and savage vigor, this warlord channels the ferocity of the Novokh Dynasty, thriving in the blood-soaked maelstrom of close combat. The Blood-Fueled Fury embodies a primal energy, drawing strength from the violence of battle. With each victorious strike, he absorbs the essence of the fight, becoming an even more formidable force on the battlefield. As he rends and tears through his enemies, his growing momentum turns him into an unstoppable engine of destruction, embodying the Novokh creed that power is drawn from the lifeblood of the foe.}

A Warlord with this Trait gains an additional Wound at the end of any Assault phase in which he inflicts at least one unsaved Wound on an enemy model. This can not increase the Warlord’s Wounds Characteristic above his starting value, but if this effect is triggered while the Warlord has his maximum possible number of Wounds then he instead gains +1 Attacks and Strength until the end of the controlling player’s next turn. In addition, an army whose Warlord has this Trait may make an additional Reaction in the opposing player’s Assault phase so long as the Warlord has not been removed as a casualty.


\subsection{Sautekh}

%TODO
\textbf{Advanced Reaction:}

\textbf{Dynasty Effect:}
Warlord has not been removed as a casualty.

\textbf{Sautekh: Hyperlogical Strategist}

One of those ones that gives a reaction in each phase, versatile commander type


\subsection{Szarekhan}

Szarekhan Dynasty Necron units gain the Necron Dynasty (Szarekhan) special rule, which grants the TODO advanced reaction and Uncanny Artifice special rule.

Any unit with the Necron Dynasty (Szarekhan) special rule may take any of the following:
\begin{itemize}
	\item Master-Work special rule on one of their weapons \dotfill +10 points.
\end{itemize}

\textbf{Advanced Reaction (Undying Empire):} This Advanced Reaction may be made once per battle in the opposing player's turn, when any enemy unit declares a Shooting Attack targeting a friendly unit under the Reactive player's control composed entirely of models with the Necron Dynasty (Szarekhan) special rule. Once the Active player has completed their attack and casualties are removed, during the resulting \quickref{Reanimation Protocols} rolls: after you have created a Reassembling Pool, double its size. After you have finished your \quickref{Reanimation Protocols} rolls, the reacting unit may immediately move a number of inches equal to twice the lowest initiative in the unit.

\textbf{Necron Dynasty (Szarekhan) (Uncanny Artifice):} Units with this special rule may give any of their weapons Master-Crafted for 10 pts/weapon. Additionally, units with this special rule gain the Stubborn special rule.

\textbf{Szarekhan:}


\subsection{Thokt}

%TODO
Any unit with the Necron Dynasty (Thokt) special rule may take any of the following:
\begin{itemize}
	\item \quickref{Radioactive Energetics} \dotfill +10 points.
	\item \quickref{Rad-Receptors} \dotfill +2 points.
\end{itemize}

\textbf{Advanced Reaction:}

\textbf{Dynasty Effect:} 

\textbf{Thokt}


\subsection{Triarch}

%TODO
Triarch Necron units gain the Triarch special rule, which grants the TODO advanced reaction and TODO special rule.

Any unit with the Triarch special rule and the Noble Sub-Type may take any of the following:
\begin{itemize}
	\item Upgrade to Triarch Executioner \dotfill +X points.
\end{itemize}

\textit{Triarch Executioner:} Add +1 to the model's BS, WS, and A.

\textit{Triarch Adjudicator:} Add +3" to the model's \quickref{Nodal Range}.

\textbf{Advanced Reaction:}

\textbf{Triarch:} TODO: More. Units with this special rule and the \quickref{Decurion Nemesor} or \quickref{Tesserarion Nemesor} special rule may also take a \quickref{Triarch Praetorian Vanguard} unit as an option for that special rule.

\textbf{Triarch:}


\subsection{Destroyer Cult}

%TODO
Madness effect? High loss effect?

\textbf{Advanced Reaction:}

\textbf{Dynasty Effect:}

\textbf{Destroyer Cult:}


\subsection{Flayed Ones}

%TODO
Anti-infantry stuff?

A Charnel Lychguard Phalanx with the Flayer Cult special rule may take the following option:

One Charnel Lychguard may take:
\begin{itemize}
	\item \quickref{Dynastic Ankh} \dotfill +10 points
\end{itemize} 

\textbf{Advanced Reaction:}

\textbf{Dynasty Effect:}

\textbf{Flayed Ones:}


\end{multicols}